### 2025-01-28 README.Rmd

<!-- badges: start -->
[![R-CMD-check](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/idem-lab/conmat?branch=master)
<!-- badges: end -->

@@

You can install the stable version from cran with:

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/conmat/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/conmat)
<!-- badges: end -->

@@

You can install the stable version from CRAN with:
